Illusion Game Validation (Study 1)

### 2022-08-05 study1.Rmd
update stim

```

@@

>>>>

# IES
df |> 
  group_by(Participant, Illusion_Type) |>
  summarize(Correct = 1-mean(Error)) |> 
  ungroup() |> 
  estimate_density(select="Correct") |> 
  plot()

df |> 
  filter(Error == 0) |> 
  group_by(Participant, Illusion_Type) |>
  summarize(RT = mean(RT)) |> 
  ungroup() |> 
  estimate_density(select="RT") |> 
  plot()
```

@@

One thing that stood out was Zöller, which seems to exhibit a non-linear relationship of illusion effect. Next study, by generating a wider range of illusion strength, will attempt at clarifying this point.
